\resumeSubHeadingListStart
    \resumeSubheading
    {Eazel Inc.}{Oct 2021 -- Jun 2022} % Changed company name format slightly
    {MLOps Engineer, MLOps}{Jung-gu, Seoul} % Translated location
        
    \resumeProjectHeading
    {\textbf{Art Market Analysis PoC}}{Apr 2022 -- Jun 2022} % Translated
    \resumeItemListStart
        \resumeItem{Quantitatively analyzed and refined artist CV data using Entity Recognition technology with HuggingFace's NLP.} % Translated
        \resumeItem{Analyzed articles using Word Histograms.} % Translated (Corrected typo)
        \resumeItem{Analyzed articles using Sentiment Analysis.} % Translated (Corrected typo)
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Instagram Relationship Data Analysis}}{Feb 2022 -- Apr 2022} % Translated
    \resumeItemListStart
        \resumeItem{Analyzed relationships using Node2Vec, K-means, and PCA techniques.} % Translated
        \resumeItem{Developed data visualization page showing directed graph relationships using NextJS, Flask, and CytoscapeJS.} % Translated
        \resumeItem{Secured Series A funding based on analysis data.} % Translated
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Instagram Relationship Information Scraper Development}}{Oct 2021 -- Jun 2023} % Translated
    \resumeItemListStart
        \resumeItem{Devised and implemented various methods for continuous data collection.} % Translated
        \resumeItem{Developed dynamic page scraper using Selenium.} % Translated
        \resumeItem{Developed data scraper via Public API using requests.} % Translated
        \resumeItem{Developed data scraper using Instagrapi, an Open Source Project utilizing Instagram's private API.} % Translated
        \resumeItem{Migrated Instagrapi (written in Python) to Swift language to develop a data scraper operating in a mobile environment}
        \resumeItem{
            Contributed to Open Source project for social relationship data collection: \href{https://github.com/subzeroid/instagrapi/graphs/contributors}{\underline{Instagrapi}} % Translated
        }
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Art Artist Information Scraper Development}}{Oct 2021 -- Nov 2021} % Translated
    \resumeItemListStart
        \resumeItem{Developed static page scraper using requests.} % Translated
        \resumeItem{Developed high-speed scraping environment by running multiple EC2 instances using boto3 and MultiThreading.} % Translated
        \resumeItem{Collected information on 600,000 artists and 3 million artist CV entries.} % Translated
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{PostgreSQL-based Collected Data Management}}{} % Translated
    \resumeItemListStart
        \resumeItem{Stored Raw Data and Purified data separately through schema separation.} % Translated
        \resumeItem{Refined data using Python and psycopg2} % Translated
    \resumeItemListEnd
\resumeSubHeadingListEnd